Self Regulation Ontology Retest Data Report

### 2017-10-31 code/SRO_Report.Rmd
added variance breakdown plot for surveys and non ddm task variables

  df = df %>% select(-dv, -sub_id)
  icc = ICC(df)
  var_breakdown = data.frame(subs = ICC(tmp)$summary[[1]][1,'Mean Sq'],
                             ind = ICC(tmp)$summary[[1]][2,'Mean Sq'],
                             resid = ICC(tmp)$summary[[1]][3,'Mean Sq'])
  return(var_breakdown)
  }

@@

for(i in 1:length(numeric_cols)){
  rel_df[numeric_cols[i], 'spearman'] <- get_spearman(numeric_cols[i]) 
  rel_df[numeric_cols[i], 'icc'] <- get_icc(numeric_cols[i])
  rel_df[numeric_cols[i], 'eta_sq'] <- get_eta(numeric_cols[i])
  rel_df[numeric_cols[i], 'sem'] <- get_sem(numeric_cols[i])
  rel_df[numeric_cols[i], 'var_subs'] <- get_var_breakdown('adaptive_n_back.mean_load.logTr')$subs
  rel_df[numeric_cols[i], 'var_ind'] <- get_var_breakdown('adaptive_n_back.mean_load.logTr')$ind
  rel_df[numeric_cols[i], 'var_resid'] <- get_var_breakdown('adaptive_n_back.mean_load.logTr')$resid
}

rel_df$dv = row.names(rel_df)
row.names(rel_df) = seq(1:nrow(rel_df))
rel_df$task = 'task'
rel_df[grep('survey', rel_df$dv), 'task'] = 'survey'
rel_df = rel_df %>%
  select(dv, task, spearman, icc, eta_sq, sem)
# row.names(rel_df) = NULL

@@

>>>>

  df = df %>% select(-dv, -sub_id)
  icc = ICC(df)
  var_breakdown = data.frame(subs = icc$summary[[1]][1,'Mean Sq'],
                             ind = icc$summary[[1]][2,'Mean Sq'],
                             resid = icc$summary[[1]][3,'Mean Sq'])
  return(var_breakdown)
  }

@@

for(i in 1:length(numeric_cols)){
  rel_df[numeric_cols[i], 'spearman'] <- get_spearman(numeric_cols[i]) 
  rel_df[numeric_cols[i], 'icc'] <- get_icc(numeric_cols[i])
  rel_df[numeric_cols[i], 'eta_sq'] <- get_eta(numeric_cols[i])
  rel_df[numeric_cols[i], 'sem'] <- get_sem(numeric_cols[i])
  rel_df[numeric_cols[i], 'var_subs'] <- get_var_breakdown(numeric_cols[i])$subs
  rel_df[numeric_cols[i], 'var_ind'] <- get_var_breakdown(numeric_cols[i])$ind
  rel_df[numeric_cols[i], 'var_resid'] <- get_var_breakdown(numeric_cols[i])$resid
}

rel_df$dv = row.names(rel_df)
row.names(rel_df) = seq(1:nrow(rel_df))
rel_df$task = 'task'
rel_df[grep('survey', rel_df$dv), 'task'] = 'survey'
rel_df = rel_df %>%
  select(dv, task, spearman, icc, eta_sq, sem, var_subs, var_ind, var_resid)
# row.names(rel_df) = NULL
```

@@

## Variance breakdown

```{r warning=FALSE, message=FALSE}
p1 = rel_df %>%
  mutate(var_subs_pct = var_subs/(var_subs+var_ind+var_resid)*100,
         var_ind_pct = var_ind/(var_subs+var_ind+var_resid)*100, 
         var_resid_pct = var_resid/(var_subs+var_ind+var_resid)*100) %>%
  select(dv, task, var_subs_pct, var_ind_pct, var_resid_pct) %>%
  gather(key, value, -dv, -task) %>%
  mutate(key = factor(key, levels = c("var_subs_pct", "var_ind_pct", "var_resid_pct")),
         dv = factor(dv, levels = dv[order(task)])) %>%
  separate(dv, c("task_group", "var"), sep="\\.",remove=FALSE,extra="merge") %>%
  mutate(task_group = factor(task_group, levels = task_group[order(task)])) %>%
  # separate(var, c("var"), sep="\\.",remove=TRUE,extra="drop") %>%
  mutate(task_group = gsub("_", " ", task_group),
         var = gsub("_", " ", var),
         var=gsub(".ReflogTr", "", var),
         var=gsub(".logTr", "", var)) %>%
  mutate(task_group = ifelse(task_group == "psychological refractory period two choices", "psychological refractory period", ifelse(task_group == "angling risk task always sunny", "angling risk task",task_group))) %>%
  mutate(task_group = gsub("survey", "", task_group)) %>%
  filter(task=="task",
         !grepl("EZ|hddm", dv))%>%
  ggplot(aes(x=var, y=value, fill=key))+
  geom_bar(stat='identity', alpha = 0.75)+
  coord_flip()+
  facet_grid(task_group~., switch = "y", scales = "free_y", space = "free_y") +
  theme(panel.spacing = unit(0.5, "lines"), 
        strip.placement = "outside",
        strip.text.y = element_text(angle=180),
        panel.background = element_rect(fill = NA),
        panel.grid.major = element_line(colour = "grey80"),
        legend.position = 'bottom')+
  #theme_bw()+  
  theme(legend.title = element_blank())+
  scale_fill_discrete(breaks = c("var_subs_pct", "var_ind_pct", "var_resid_pct"),
                    labels = c("Variance between individuals",
                               "Variance between sessions",
                               "Error variance"))+
  ylab("")+
  xlab("")

p2 = rel_df %>%
  mutate(var_subs_pct = var_subs/(var_subs+var_ind+var_resid)*100,
         var_ind_pct = var_ind/(var_subs+var_ind+var_resid)*100, 
         var_resid_pct = var_resid/(var_subs+var_ind+var_resid)*100) %>%
  select(dv, task, var_subs_pct, var_ind_pct, var_resid_pct) %>%
  gather(key, value, -dv, -task) %>%
  mutate(key = factor(key, levels = c("var_subs_pct", "var_ind_pct", "var_resid_pct")),
         dv = factor(dv, levels = dv[order(task)])) %>%
  separate(dv, c("task_group", "var"), sep="\\.",remove=FALSE,extra="merge") %>%
  mutate(task_group = factor(task_group, levels = task_group[order(task)])) %>%
  separate(var, c("var"), sep="\\.",remove=TRUE,extra="drop") %>%
  mutate(task_group = gsub("_", " ", task_group),
         var = gsub("_", " ", var)) %>%
  mutate(task_group = ifelse(task_group == "psychological refractory period two choices", "psychological refractory period", ifelse(task_group == "angling risk task always sunny", "angling risk task",task_group))) %>%
  mutate(task_group = gsub("survey", "", task_group)) %>%
  filter(task=="survey")%>%
  ggplot(aes(x=var, y=value, fill=key))+
  geom_bar(stat='identity', alpha = 0.75)+
  coord_flip()+
  facet_grid(task_group~., switch = "y", scales = "free_y", space = "free_y") +
  theme(panel.spacing = unit(0.5, "lines"), 
        strip.placement = "outside",
        strip.text.y = element_text(angle=180),
        panel.background = element_rect(fill = NA),
        panel.grid.major = element_line(colour = "grey80"),
        legend.position = 'bottom')+
  #theme_bw()+  
  theme(legend.title = element_blank())+
  scale_fill_discrete(breaks = c("var_subs_pct", "var_ind_pct", "var_resid_pct"),
                    labels = c("Variance between individuals",
                               "Variance between sessions",
                               "Error variance"))+
  ylab("")+
  xlab("")

g_legend<-function(a.gplot){
  tmp <- ggplot_gtable(ggplot_build(a.gplot))
  leg <- which(sapply(tmp$grobs, function(x) x$name) == "guide-box")
  legend <- tmp$grobs[[leg]]
  return(legend)}

mylegend<-g_legend(p1)

p3 <- arrangeGrob(arrangeGrob(p1 +theme(legend.position="none"),
                         p2 + theme(legend.position="none"),
                         nrow=1),
             mylegend, nrow=2,heights=c(10, 1))

ggsave('Variance_Breakdown_Plot.jpg', plot = p3, device = "jpeg", path = "/output/figures/", width = 24, height = 20, units = "in")
```
